\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage{fontawesome}
\usepackage[left=0.6in,top=0.2in,right=0.6in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Alec Adub} 
\address{\faGithub: /alecadub \faEnvelope: adub.alec@gmail.com \faLinkedin: /in/alec-adub-a96587150/ \faPhone:  450-821-3497} % contact info
\begin{document}

\begin{rSection}{Skills}
{\bf Programming languages:}
Java, Typescript, PHP, C++, Python.\\
{\bf Tools and Technologies:}
React, Angular, Vue, Laravel, Spring, React-native, Ionic, Expo, Eloquent, Git, JUnit 5, Mockito, Jest, Docker, CircleCI, SonarCloud, Jira, Windows, Linux, Photoshop, Illustrator, LaTeX. \\
{\bf Languages:}
Fluent in French and English, written and spoken.
\end{rSection}

\begin{rSection}{Education}

{\bf Concordia University} \hfill {\em 2017 - 2021} 
\\ Bachelor of Engineering, Software.
\end{rSection}

\begin{rSection}{Work Experience}

\begin{rSubsection}{Software Developer, Ubisoft}{Ma 2021 - Present}{}
TTechnologies used: Typescript, Node, Jest, Electron.\\
- Create command line interface and tooling for frontend team.\\
- Develop micro applications for ecommerce inside uplay platform. \\
- Develop micro-frontends, new experiences and AB Tests
\end{rSubsection}

\begin{rSubsection}{Backend developer Intern, Coveo}{January 2021 - May 2021}{}
TTechnologies used: Java, Junit 4, Docker, MySQL.\\
- Work on a day to day basis in a micro-services architecture.\\
- Develop and release crucial features for their migration service, \\
which work as their own infracture as code for their cloud platform.
\end{rSubsection}

\begin{rSubsection}{Full stack developer, XGuard}{May 2020 - January 2021}{}
TTechnologies used: Typescript, PHP, React, Laravel, Eloquent, MySQL, React-Native.\\
- Team lead on small projects that required to create REST API's and mobile applications.\\
- Worked in a startup environment on a day to day basis. (Tight deadline, Production expected)
\end{rSubsection}

\begin{rSubsection}{Full stack developer, Cogeco}{April 2019 - May 2020}{}
TTechnologies used: Typescript, PHP, Angular, Symfony, Doctrine, MySQL, Docker.\\
- Implement features into the company websites and mobile app.\\
- Add and research libraries to satisfy requirements and increment the websites revenues.\\
- Worked in an agile environment on a day to day basis. (Scrum, Peer programming)
\end{rSubsection}

\begin{rSubsection}{Developer/Tester, Lockheed Martin}{June 2018 - March 2019}{}   TTechnologies used: Java, JUnit5, Mockito.\\
- Refactor a lot of classes to make them clean and testable.\\
- Refactor legacy code-base using design patterns.\\
- Write Unit tests, requirements, and procedures.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Projects and Awards}

{\bf BSafe (Hackatown2020, Hackathon at Polytechnique) - Winner}\hfill {\em Ionic/Python}\\
Winning project for the "AI and Data Science" category and 3rd place \\ overall, Bsafe gives you a safe route between point A and B. (400 participants)\\ \\
{\bf Harmless Buddy (ConUHacks V, Hackathon at Concordia) - Winner}\hfill {\em Ionic/Python}\\
Winning project for the category "Best use of google cloud" at ConUHacks V! \\Harmless Buddy records a meeting and highlights which sentences were condescending \\or harmful. (800 participants)

\end{rSection}

\end{document}